\Trill: Secure firewall-traversing networking

### 2012-12-14 6.858/paper/paper.tex
Finishing server section

Our implementation of \Trill has two major components: a client library for
connecting to peers, and a set of server implementations which handle the
secure, federated message routing.

@@

The actual process of ``logging in'' requires a client to send the login server
a X.509 certificate signing request (CSR).  The login server, if it so chooses,
can then endorse the client's identity by signing a cert and returning it to
the user.  The client uses cert whenever it connects to \Plume protocol servers
or to peers in order to assert its identity.  These servers and parties can
then walk their way up the chain of trust to verify the user's identity and the
authority of the login server that endorsed it.

With this cert, the client is then able to connect to the \Plume protocol
servers.  These servers will only talk over TLS to clients with valid
identities (connections to the login servers are also secured by TLS, but only
the login server's cert is used).  These \Plume servers server two major
purposes:

\begin{enumerate}
  \item Message routing.  Clients can ask their \Plume servers to pass messages
    to peers.  If they are on the same domain and are connected to the server,
    the message is routed directly; otherwise, the message is forwarded first
    to the proper server
\end{enumerate}

Discovery of server addresses and ports

>>>>

Our implementation of \Trill has two major components: a client library for
connecting to peers, and a set of server implementations (the \Plume servers)
which handle the secure, federated message routing.

@@

The actual process of ``logging in'' requires a client to connect to the login
server---over TLS-secured TCP using the login server's X.509 cert---send the
login server a certificate signing request (CSR).  The login server, if it so
chooses, can endorse the client's identity by signing a cert and returning it
to the client.  The client then uses cert whenever it connects to \Plume
protocol servers or to peers in order to assert its identity.  These servers
and parties can then walk their way up the chain of trust to verify the
client's identity and the authority of the login server that endorsed it.

With this cert, the client is then able to connect to the \Plume protocol
servers (or simply, \Plume servers).  These servers will only talk over TLS to
clients with valid identities.  These \Plume servers server two major purposes:

\begin{enumerate}
  \item \textbf{Message routing.}  Clients can ask their \Plume servers to pass
    messages to peers.  If they are on the same domain and are connected to the
    server, the message is routed directly; otherwise, the message is forwarded
    first to the proper server.  Messages generally take the format of an
    opstring, the peer's handle, the sender's cert, and a payload.

  \item \textbf{UDP reflection.}  Before connecting to a peer, a client can
    open up an ephemeral UDP port for listening and ask its \Plume server to
    identify its IP and port, since firewalls may prevent the client from
    finding out on its own.  In this protocol, the client first sends the
    server a random 64-bit number alongside a reflection request.  The server
    hashes this number with the client's handle and sends the client an ack.

    At this point, the client begins regularly pinging the server with UDP
    datagrams containing the random number.  When the server receives a UDP
    packet that matches a client who has requested UDP reflection, it
    determines the IP and port the client was sending on and returns it, over
    TCP, back to the client, who saves it and halts UDP transmission.
\end{enumerate}

There are two major types of \Trill messages, corresponding to requests a
client makes of its peer, that \Plume servers are responsible for routing:

\begin{enumerate}
  \item \textbf{Connect.}  To connect to a peer, a client first prepares a
    payload used to identify itself---we colloquially refer to this as a
    ``calling card.''  This calling card consists of the IP and port of the
    client's UDP listener, signed by the client's identity certificate, and
    then encrypted by the peer's public key.  Signing the cert enables the peer
    to confirm the association between the client and the given IP and port.
    Encryption lets the client keep its IP and port secret from other domains'
    \Plume servers, which it may not trust.  (As clients, we necessarily have
    to trust other domains to make correct endorsements of identity, but we can
    also verify these endorsements out-of-band with our peers).

    Encryption also prevents replay attacks in the event that someone who isn't
    our peer obtains our calling card.  Passing just the signed IP and port
    would allow an adversary to forge connection requests in our name, which
    could flood us with connection responses.  Encryption makes it so that only
    our peer can do so.

  \item \textbf{Identify.}  If a client wishes to connect to a peer, it needs
    to obtain the peer's public key in order to encrypt a calling card.  In
    addition to connection requests, client's can also make identification
    requests of their peers.  Willing peers can simply pass their cert back to
    the requesting client, who can then initiate connection.
\end{enumerate}

Discovery of server addresses and ports is done via DNS queries for SRV
records; we specify the use of \verb`_plume` and \verb`_plume-login`, both over
TCP, for the \Plume and login servers, respectively, and \verb`_plume-udp` for
the UDP reflection service.  All messages sent over the wire are marshalled
using \textsc{MessagePack}.

Once two peers have exchanged calling cards, they can then use the \Trill
library to establish a secured UDP connection.
